---
title: "open_loop_results_eda"
author: "Ilmar Uduste"
date: "5/5/2022"
output: html_document
---

```{r}
library(ggplot2)
library(plyr)
library(dplyr)
library(gghighlight)
library(tidyr)
```

```{r}
df <- read.csv(file = "test_ground_truth_and_predictions.csv", sep = ";")
df_fixed <- read.csv(file = "test_ground_truth_and_predictions_fixed.csv", sep = ";")
df$tub_name <- mapvalues(df$tub_name, from = c("tub_89", "tub_168", "tub_175"), to = c("Test A", "Test B", "Test C"))
df$tub_name <- df$tub_name %>% 
  factor(levels = c("Test A", "Test B", "Test C"))

df$model_name_short <- mapvalues(df$model, 
                                 from = c("frameshifted_-2", "frameshifted_-1", "lowres",
                                          "frameshifted_1", "frameshifted_2", "frameshifted_3", "frameshifted_4"), 
                                 to = c("FS -2", "FS -1", "FS 0", "FS 1", "FS 2", "FS 3", "FS 4"))
df$model_name_short <- df$model_name_short %>% 
  factor(levels = c("FS -2", "FS -1", "FS 0", "FS 1", "FS 2", "FS 3", "FS 4"))


df_fixed$tub_name <- mapvalues(df_fixed$tub_name, from = c("tub_89", "tub_168", "tub_175"), to = c("Test A", "Test B", "Test C"))
df_fixed$tub_name <- df_fixed$tub_name %>% 
  factor(levels = c("Test A", "Test B", "Test C"))

df_fixed$model_name_short <- mapvalues(df_fixed$model, 
                                 from = c("frameshifted_-2", "frameshifted_-1", "lowres",
                                          "frameshifted_1", "frameshifted_2", "frameshifted_3", "frameshifted_4"), 
                                 to = c("FS -2", "FS -1", "FS 0", "FS 1", "FS 2", "FS 3", "FS 4"))
df_fixed$model_name_short <- df_fixed$model_name_short %>% 
  factor(levels = c("FS -2", "FS -1", "FS 0", "FS 1", "FS 2", "FS 3", "FS 4"))
```

```{r}
cleaned_lap <- df %>% 
  filter(deleted_index == "False")

cleaned_lap_fixed <- df_fixed %>% 
  filter(deleted_index == "False")

```

# Mean absolute difference between frameshifted models in the same frame

# Mean absolute difference across the whole dataset between frameshifted models and original

```{r}
cleaned_lap$mae <- abs(cleaned_lap$angles - cleaned_lap$user.angle)
cleaned_lap$mse <- (cleaned_lap$angles - cleaned_lap$user.angle)**2
cleaned_lap_fixed$mae <- abs(cleaned_lap_fixed$angles - cleaned_lap_fixed$user.angle)
cleaned_lap_fixed$mse <- (cleaned_lap_fixed$angles - cleaned_lap_fixed$user.angle)**2
```

```{r}
cleaned_lap$mae
```

```{r}
merge(
  cleaned_lap %>% 
    select(angles, frame_indexes, tub, model, user.angle, mae),
  cleaned_lap_fixed %>% 
    select(angles, frame_indexes, tub, model, user.angle, mae),
  by = c("frame_indexes", "tub", "model"),
  suffixes = c("_orig", "_fixed")
) %>% 
  mutate
```


```{r}
cleaned_lap %>% 
  ggplot(aes(x = mae)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_vline(xintercept = -1, linetype = "dashed", color = "gray")+
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray")+
  geom_vline(xintercept = 2, linetype = "dashed", color = "gray")+
  geom_histogram(binwidth = 0.1, aes(y = ..density..), color = "#ff7c43", fill = "#ff7c43") +
  theme_minimal() +
  facet_grid(tub_name ~ model_name_short) +
  labs(x = "Steering Angle", title = "Histogram of the Mean Absolute Error of Steering Angle Predictions from \nFrameshifted Models compared to Ground Truth")
```

```{r}
cleaned_lap_fixed %>% 
  ggplot(aes(x = mae)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_vline(xintercept = -1, linetype = "dashed", color = "gray")+
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray")+
  geom_vline(xintercept = 2, linetype = "dashed", color = "gray")+
  geom_histogram(binwidth = 0.1, aes(y = ..density..), color = "#ff7c43", fill = "#ff7c43") +
  theme_minimal() +
  facet_grid(tub_name ~ model_name_short) +
  labs(x = "Steering Angle", title = "Histogram of the Mean Absolute Error of Steering Angle Predictions from \nFrameshifted Models compared to Ground Truth")
```

```{r}
cleaned_lap %>% 
  ggplot(aes(x = model_name_short, y = mae)) +
  geom_violin(fill = "#ffa600") +
  # geom_violin(aes(fill = model_name_short)) +
  geom_boxplot(width = 0.1, alpha = 0.9) +
  theme_minimal() +
  labs(x = "Frameshifted Model", y = "Mean Absolute Error", title = "Distribution of the Mean Absolute Error of Steering Angle Predictions\nfrom Frameshifted Models compared to Ground Truth")

ggsave("plots/mae_distribution.png", width = 6, height = 4)
```
Explain how the mean is not important here, but since every mistake stacks, then the upper bounds (quartiles are important)

```{r}

```


# MSE
```{r}
cleaned_lap %>% 
  ggplot(aes(x = model_name_short, y = mse)) +
  geom_violin(fill = "#ffa600") +
  # geom_violin(aes(fill = model_name_short)) +
  geom_boxplot(width = 0.1, alpha = 0.9) +
  theme_minimal() +
  labs(x = "Frameshifted Model", y = "Mean Squared Error", title = "Distribution of the Mean Squared Error of Steering Angle Predictions\nfrom Frameshifted Models compared to Ground Truth")

ggsave("plots/mse_distribution.png", width = 6, height = 4)
```
# Proportion of MAE that is over 1 for each model

```{r}
cleaned_lap %>% 
  ggplot(aes(x = model_name_short, y = mae)) +
  geom_violin(fill = "#ffa600") +
  # geom_violin(aes(fill = model_name_short)) +
  geom_boxplot(width = 0.1, alpha = 0.9) +
  gghighlight(mae >= 1) +
  theme_minimal() +
  labs(x = "Frameshifted Model", y = "Mean Absolute Error", title = "Distribution of the Absolute Error of Steering Angle Predictions\nfrom Frameshifted Models compared to Ground Truth")

```

# Histogram of all models turning angles
```{r}
cleaned_lap %>% 
  ggplot(aes(x = angles)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_vline(xintercept = -1, linetype = "dashed", color = "gray")+
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray")+
  geom_histogram(binwidth = 0.1, aes(y = ..density..), color = "#ff6361", fill = "#ff6361") +
  theme_minimal() +
  facet_grid(tub_name ~ model_name_short) +
  scale_x_continuous(breaks = c(-1, 0, 1)) +
  labs(x = "Steering Angle", title = "Histogram of Steering Angle Predictions from Frameshifted Models on Test Tubs")


ggsave("plots/steering_histogram.png", width = 6, height = 4)
```
```{r}
cleaned_lap %>% 
  ggplot(aes(x = angles)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_vline(xintercept = -1, linetype = "dashed", color = "gray")+
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray")+
  geom_histogram(binwidth = 0.1, aes(y = ..density..), color = "#ff6361", fill = "#ff6361") +
  theme_minimal() +
  facet_wrap(~ model_name_short, ncol = 7) +
  scale_x_continuous(breaks = c(-1, 0, 1)) +
  labs(x = "Steering Angle", title = "Histogram of Steering Angle Predictions from Frameshifted Models\non Test Tubs")

ggsave("plots/test_histogram.png", width = 6, height = 2)
```

Create a rounded dataset!!!
Rounded to nearest 0.25

```{r}
cleaned_lap$angles_rounded_025 <- round(cleaned_lap$angles*4)/4
cleaned_lap$angles_rounded_050 <- round(cleaned_lap$angles*2)/2
cleaned_lap$angles_rounded_1 <- round(cleaned_lap$angles)

rounded_cleaned_lap <- cleaned_lap %>% 
  gather(rounding, angle_value, angles, angles_rounded_025, angles_rounded_050, angles_rounded_1)

rounded_cleaned_lap$rounding <- factor(rounded_cleaned_lap$rounding, 
                                       levels = c("angles", "angles_rounded_025", 
                                                  "angles_rounded_050", "angles_rounded_1"),
                                       labels = c("Original", "Nearest 0.25", "Nearest 0.5", "Nearest 1"))

rounded_cleaned_lap %>%
  ggplot(aes(x = angle_value)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "darkgray")+
  geom_vline(xintercept = -1, linetype = "dashed", color = "gray")+
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray")+
  geom_histogram(aes(y = ..density..), color = "#ff6361", fill = "#ff6361") +
  theme_minimal() +
  facet_grid(rounding ~ model_name_short) +
  scale_x_continuous(breaks = c(-1, 0, 1)) +
  scale_y_continuous(breaks = c(0, 5, 10)) +
  labs(x = "Steering Angle", title = "Steering Angle Predictions on Test Tubs from Frameshifted Models")


ggsave("plots/rounded_histogram.png", width = 6, height = 4)
```

```{r}
as.integer(1.6)
```


```{r}
cleaned_lap %>% 
    ggplot(aes(x = user.angle)) +
  geom_histogram(aes(y = ..density..)) +
  theme_minimal() +
  facet_wrap(~ tub) 
```
# Timegraph

```{r}
cleaned_lap %>% 
  filter(tub_name == "Test A") %>% 
  filter(frame_indexes > 21072 & frame_indexes < 21752) %>% # Laps 20909, 21072, 21239, 21412, 21583, 21752
  ggplot(aes(x = frame_indexes, y = user.angle)) +
  geom_line() +
  theme_minimal()

```
Get correct indexes from tub laps excel

```{r}
cleaned_lap %>% 
  filter(tub_name == "Test A") %>% 
  filter(frame_indexes > 21072 & frame_indexes < 21583) %>% # Laps 20909, 21072, 21239, 21412, 21583, 21752
  ggplot(aes(x = frame_indexes, y = angles, color = model_name_short)) +
  geom_line(data = cleaned_lap %>% 
    filter(tub_name == "Test A") %>% 
    filter(frame_indexes > 21072 & frame_indexes < 21583),
    aes(x = frame_indexes, y = user.angle), color = "black", alpha =0.9) +
  geom_line(show.legend = FALSE, size = 1.1, alpha = 0.7) +
  theme_minimal() +
  facet_wrap(~model_name_short, nrow = 7, strip.position="right") +
  labs(x = "Frame Index", y = "Predicted/Ground Truth Steering Angle", color = "Frameshifted Model", title = "Timegraphs: Ground Truth Steering vs Predicted Steering") +
  scale_y_continuous(breaks = c(-1, 0, 1)) +
  scale_x_continuous(label = scales::comma)

ggsave("plots/timegraph_steering.png", width = 6, height = 6)

```

